Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.

>>>>

---> Education system reinforcing self-confidence

---> Higher degree of individual self-confidence

---> Higher probability an individual will become an entrepreneur

---> higher rate of entrepreneurship at a country-level.
